---
title: "Homework 2"
author: Tu  Nguyen
output: github_document
---

This is my solution to HW2.


```{r, message = FALSE}
library(tidyverse)
```

## Problem 2

Read in the subway dataset and some brief cleaning

```{r}
subway_data = 
  read_csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>% 
  select(-(ada_notes:entrance_location))  %>% 
  select(-c("division", "exit_only", "staffing", "staff_hours")) %>% 
  mutate(entry = recode(entry, `YES` = "TRUE", `NO` = "FALSE"))
```

After some brief cleaning, the data contains subway line, station name, station latitude/longitude, routes served, entry, vending, entrance type, and ADA compliance. `select` function was used to remove the columns after ADA. `select` was then used a gain to remove some unneccessary columns. `mutate` function was used to change from character variable to logical variable. 

The resulting dataset is a tibble of `r ncol(subway_data)` columns and `r nrow(subway_data)` rows (1,868 x 18). These data are not tidy. 

Subway dataset without `entrance type`, `entry`, and `vending`
```{r}
subway_df = select(subway_data, -(entrance_type:vending))
```

Number of distinct subway stations
```{r}
subway_data_tidy = 
  distinct(subway_df)
```
There are `r nrow(subway_data_tidy)` distinct stations. 

Number of stations are ADA compliant
```{r}
subway_ada_compliant = filter(subway_data_tidy, ada == TRUE)
```
There are `r nrow(subway_ada_compliant)` stations that ADA compliant. 

Proportion of station entrances/exits without vending allowance
```{r}
subway_no_vending = filter(subway_data, vending == "NO")
subway_no_vending_distinct = distinct(subway_no_vending, line, station_name, vending)
```
Proportion of station entrances/exits without vending allowance is `r nrow(subway_no_vending_distinct)`. 


```{r}
subway_reformat = 
  gather(subway_data_tidy, `route1`:`route11`, key = "route", value = "subway_line") %>% 
  select(-route)

A_line = filter(subway_reformat, subway_line == "A")
A_line_compliant = filter(A_line, ada == "TRUE")
```
There are `r nrow(A_line)` distinct stations serve the A train, in which `r nrow(A_line_compliant)` are ADA compliant. 

## Problem 3

Read in pols month dataset. 

```{r}
poll = 
  read_csv("./data/fivethirtyeight_datasets/pols-month.csv") %>% 
  separate(mon, into = c("year", "month", "day"), sep = "-") %>% 
  relocate(prez_dem, .after = prez_gop) %>% 
  pivot_longer(
    prez_gop:prez_dem,
    names_to = "prez",
    values_to = "president"
  ) %>% 
  select(-c(prez, day))
```













