---
title: "Homework 1"
author: Tu  Nguyen
output: github_document
---

This is my solution to HW1.


```{r, message = FALSE}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.
```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame. 

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of numbers and logical but not character or factor. 

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp_gt_0)
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```


## Problem 2

Load the *penguins* dataset

```{r}
data("penguins", package = "palmerpenguins")
```


* Penguins dataset contains a collection of variables in the columns and characteristics of each variable (species, island, body mass, sex, length, depth)

* The penguins data frame has *`r nrow(penguins)`* *rows* and *`r ncol(penguins)`* *columns*. 

* The *mean* of the flipper length of penguins dataset is *`r mean(penguins)`*. 


This code chunk below generates a scatterplot and save it.

```{r flipper_length and bill_length plot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_plot_penguins.pdf", height = 5, width = 5)
```
The plot shows different of values of *flipper length* and *bill length* of Adelie, Chinstrap, and Gentoo species. 







